Meta-analysis

### 2019-10-30 05_MetaAnalysis.Rmd
Cleaning up the grainyield x rainfall regression. moving code to a script file

```{r rainfall_sum_Sstart}
# add column for sum in-crop rainfall
rain_dat_sum$rainfall_sum <- NA

# source funtion that uses bomrang get_historical to return the sum rainfall between two dates
source("R/AUS_rainfall_function.r")

# loop to download and save all the rainfall sum data
# this first loop Investigate when is the first day in the season for which in-crop rainfall is important

# use Bomrang to find the quantaty of rain for the season and do a linear regression
for(k in -19:20){
for(j in -9:30){

   lm_rain <- data.frame(start_day = rep(-20:40, times = length(-30:30)),
              end_day = rep(-30:30, each = length(-20:40)),
              lm_pval = NA,
              lm_rsquared = NA,
              lm_adj_rsquared = NA
   )
   dim(lm_rain)

# for using parRapply   
#    cl8 <- makeCluster(getOption("cl.cores", 8))
# clusterExport(cl8, list("rain_dat_sum", "AUS_rainfall", "lm_rain", "get_historical"))

   testlist1 <- apply(lm_rain,1,function(x1){
         for(i in seq_along(rain_dat_sum$trial_ref)){

         rain_dat_sum$rainfall_sum <- AUS_rainfall(StartDate = as.Date(rain_dat_sum$planting_date)[i] + x1[1],
                                                   EndDate = as.Date(rain_dat_sum$planting_date[i]) + 80 + x1[2],
                                                   lat = rain_dat_sum$lat[i],
                                                   long = rain_dat_sum$lon[i])
         }
         lmod1 <- summary(lm(rainfall_sum ~ grain_yield, 
                       data = rain_dat_sum[rain_dat_sum$location != "Hermitage",])) # remove hermitage which is irrigated

         pval <- coef(lmod1)[2,4]
         rsqu <- lmod1$r.squared
         ADrs <- lmod1$adj.r.squared
         return(list(pval,rsqu,ADrs))

         })

head(testlist1)   
lm_rain$lm_pval <- head(bind_rows(testlist1))
   ?bind_rows

for(i in seq_along(testlist1)){
   lm_rain$lm_pval[i] <- testlist1[[i]][[1]]
   lm_rain$lm_rsquared[i] <- testlist1[[i]][[2]]
   lm_rain$lm_adj_rsquared[i] <- testlist1[[i]][[3]]
}
head(lm_rain)

@@

   if(k == -19 & j == -19){
      lm_pval <- matrix(nrow = 40,
                        ncol = 40)
      colnames(lm_pval) <- as.character(-19:20) # End date
      row.names(lm_pval) <- as.character(-9:30) # start date

      lm_square <- matrix(nrow = 40,
                          ncol = 40)
      colnames(lm_square) <- as.character(-19:20) # End date
      row.names(lm_square) <- as.character(-9:30) # start date
      }

         rain_dat_sum$rainfall_sum[i] <- 
            AUS_rainfall(StartDate = (as.Date(rain_dat_sum$planting_date)[i] + j),
                         EndDate = (as.Date(rain_dat_sum$planting_date)[i] + 80 + k ),
                         lat = rain_dat_sum$lat[i],
                         long = rain_dat_sum$lon[i])

      lm_pval[j,k] <- coef(lmod1)[2,4]
      lm_square[j,k] <- lmod1$r.squared

   }
   }# If it aborts with an error Error in row_start:(row_start + season) : argument of length 0, just re-run the code

>>>>

```{r rainfall_sum_Sstart}
#!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
#!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
#
#       BEWARE THIS CODE REQUIRES MORE WORK AND TAKES ~10 HOURS TO RUN
#
# !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
# !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

source("R/Rainfall_x_cropYield.R")
head(lm_rain)
lm_rain <- read.csv("data/lmInSeasonRainfall.csv",stringsAsFactors = FALSE)

@@
